---
title: "DSA5041 Project Vignette"
author: "Robert Hill"
date: "4/15/2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DSAProjVig}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The package `DSA5041PROJ1` runs the Student's T-Test on two populations to determine if the means are the same.

# Functions

`myttest` takes in two populations of data, whether the populations are paired, and an alpha value (measure of error). The function then runs the appropriate form of the T-Test and returns all relevant information in an Rttest object.
`Rttest.print` is the generic print function for Rttest objects. This function prints the confidence interval of the T-Test.
`Rttest.plot` is the generic plot function for Rttest objects. This function plots one or two boxplots, depending on whether the data is paired. If the data is paired, the confidence interval is shown as well.

## OOP

In this package we will be using `S3` OOP -- which is the commonly used object oriented form in R package making.

See <https://adv-r.hadley.nz/s3.html> for more information.

## Documentation

There are two forms of documentation
  
  1. Function specific using Roxygen.
  2. Vignette -- long form.
  
# Constructor

The first function is `myttest`. It runs a t-test and produces a list of useful information, including the population data, type of T-Test used, and the p-value.

```{r, eval=FALSE}
myttest=function(x, y, paired=FALSE, alpha=0.05){

  ###conditionals to check arguments
  #confirming x is a numeric vector
  xClass = class(x)
  if(xClass != "numeric") {
    stop(paste0("The input x is of class ", xClass, " but must be a vector!!"))
  }
  #confirming y is a numeric vector
  yClass = class(y)
  if(yClass != "numeric") {
    stop(paste0("The input y is of class ", yClass, " but must be a vector!!"))
  }
  #confirming paired is a boolean
  pClass = class(paired)
  if(pClass != "logical") {
    stop(paste0("The input paired is of class ", pClass, " but must be either TRUE or FALSE!!"))
  }
  #confirming alpha is between 0-1
  if(alpha < 0 || alpha > 1) {
    stop(paste0("The input alpha is out of bounds. Input a value for alpha between 0 and 1"))
  }


  ####Building out the dataframe
  #declaring vectors for data and the source "v". Code from the example.
  data <- vector(mode = "numeric", length = length(x) + length(y))
  v <- vector(mode = "list", length = length(data))

  #creating dataframe
  data <- c(x,y)
  v <- rep(c("x","y"), c(length(x),length(y)))
  df = data.frame("data" = data, "v" = v)


  ####Checking sample varience to determine which type of ttest to run
  #Once checked, the ttest is run.

  tTestType <- ''
  tt <- ''

  if(paired) {
    tTestType <- "Paired"
    tt<-t.test(x,y,mu=0, paired = TRUE)
  }
  else {

    #testing the variances. If the pvalue is > than alpha, then we assume they are equal.
    varTest <- var.test(x,y)
    varEqual <- varTest$p.value > alpha

    #if var is equal
    if(varEqual){
      tTestType <- "T-test"
      tt<-t.test(x,y,var.equal = TRUE)#,conf.level=1-alpha)
    }

    #if var is not equal
    else {
      tTestType <- "Welch"
      tt<-t.test(x,y,var.equal = FALSE)#,conf.level=1-alpha)
    }
  }


  #based on the ttest p-value, we accept or reject the Null
  result = 'N'
  if(tt$p.value < alpha) {
    result = 'Y'
  }

  #returning a list
  returnObject = list('testType' = tTestType,
                      'result' = result,
                      'statistics' = tt,
                      'data' = df,
                      'pvalue'=tt$p.value)
  class(returnObject) = "Rttest"
  returnObject
}
```

Below is an example of the `myttest` function running:

```{r}
library(DSA5041PROJ1)
set.seed(21)
x <- rnorm(30,5,2)
set.seed(23)
y <- rnorm(30,3,2)
alpha <- 0.05

obj <- myttest(x=x, y=y, paired=F, alpha=alpha)
class(obj)

```

Notice that the output is of class "Rttest"

The Rttest object is a list of relevant information:

```{r}
obj$testType
obj$result
obj$statistics
obj$data
obj$pvalue

```

The components can then be operated on by an appropriate method attached to a generic.

# Methods

## Print

This method is attached to the generic function `print()`. This function prints the confidence interval for an Rttest object.

```{r, eval=FALSE}
print.Rttest <- function(x, ...) {

  #though it shouldn't ever happen, the method confirms that an Rttest object is given as the argument
  stopifnot(class(x) == "Rttest")

  #generating table kable styled
  output <- paste("The confidence interval for the difference between the sample means is: ",
        x$statistics['conf.int'])
  output

}
```

We can call it by simply invoking the `print()` function

```{r}
print(obj)
```

## Plot

This method is attached to the generic function `plot()`. This function plots the data that was supplied when creating a Rttest object, if the data is non-paired. The plot is of two boxplots. However, if the data is paired, one boxplot of the difference of data is shown, with the confidence interval overlayed in yellow.

```{r, eval=FALSE}
plot.Rttest <- function(x, ...) {

  #though it shouldn't ever happen, the method confirms that an Rttest object is given as the argument
  stopifnot(class(x) == "Rttest")

  plotIt <- ''

  #checking to see if the ttest was paired
  if(x$testType == "Paired") {

    #since it's paired, we take the difference between the samples
    dataDiff <- x$data[x$data[,2]=='x',1] - x$data[x$data[,2]=='y',1]

    #and plot it as a boxplot
    plotIt <- ggplot(x$data[x$data[,2]=='x',], aes(x=rep("x",length(dataDiff)),y=dataDiff)) +
      geom_boxplot() +
      geom_errorbar(aes(ymin=x$statistics$conf.int[1],ymax=x$statistics$conf.int[2]), color="yellow", size=1) +
      labs(x="Values", y="Difference between paired samples")
  }
  else {

    #generating boxplots
    plotIt <- ggplot(x$data, aes(x=x$data[,2],y=x$data[,1],fill=x$data[,2])) +
      geom_boxplot() +
      labs(x="Population", y="Values")
  }

  plotIt

}
```

We can call it by simply invoking the `plot()` function

```{r}
plot(obj)
```




# Shiny server

These two functions have been placed into a shiny app and can be invoked using 

```{r,eval = FALSE}
#shinyhist()
```

